---
title: "Demographics"
output: 
  html_document

---

<!-- Set general settings -->

```{r setup, include = FALSE}

# Set general settings for markdown file
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  comment = "",
  results = "hold"
)


# Clear environment
rm(list = ls())


# Enable/disable caching of time-consuming code chunks
knitr_cache_enabled = TRUE


# Load packages
library(dplyr)      # for data manipulation
library(knitr)      # for integrating computing and reporting in markdown
library(kableExtra) # for customizing appearance of tables
library(foreign)    # for reading in SPSS file
library(tidyr)      # for gather and spread function
library(lubridate)  # to convert seconds to minutes and seconds


# Load functions
source("./functions/my_table_template.R") # Function to create table template


# Turn off scientific notation
options(scipen = 999)
```
<br><br> 

## Sample Overview
***

* N = 56 (N HC = 28, N OCD = 28)

* OCD and HC matched for gender, age, education level, and handedness 

* Native German speakers with normal or corrected-to-normal vision

* Patients with OCD were recruited from the outpatient clinic at Humboldt-Universität zu Berlin. All patients were interviewed and diagnosed by trained psychologists using the Structured Clinical Interview for DSM-IV (SCID-I; Wittchen et al., 1997) and met the DSM-IV criteria for OCD as primary disorder. 

* Exclusion criteria 
  - general: history of any neurological disorder, current or lifetime diagnosis of a substance-related disorder, schizophrenia spectrum disorder, bipolar disorder, use of benzodiazepines during the last week or of neuroleptic medication during last three months, and general exclusion criteria for tDCS (e.g., any metal or electronic implants in the head or upper body, skin disorder or skin condition at or near stimulation locations, pregnancy)
  - HC: self-reported history of any current or past axis I disorder or psychotherapeutic treatment

```{r demographics}

# Load data 
participant_data <- read.spss("./data/Probandendaten.sav", to.data.frame = TRUE)
questionnaires   <- read.spss("./data/psychoEQExport.sav", to.data.frame = TRUE, add.undeclared.levels = "no") # add.undeclared.levels required to prevent irrelevant warning message


# Select relevant variables
participant_data <- participant_data[,c("Code","Alter","Geschlecht","Schulabschluss","Händigkeit","Komorbidität_1","Komorbidität_2",
                                        "Komorbidität_3","Medikamente_JaNein","SSRI","SNRI","Trizykl_Antidepressiva",
                                        "Kombination_SSRI_Antidepressiva","YBOCS_gesamt","YBOCS_Gedanken","YBOCS_Handlungen","MADRS", "WST",
                                        "Dauer_nach_tDCS_bis_Flanker_T1","Dauer_nach_tDCS_bis_Flanker_T2","Tage_zw_Sessions")]
questionnaires   <- questionnaires[,c("CODE", "BD2SUMT0", "OCISUMT0", "STSSUMT0", "STTSUMT0")] 


# Merge dataframes and rename columns
participant_data$Code <- gsub(" ", "", participant_data$Code , fixed = TRUE) # delete empty spaces from string to enable merging
demographics <- left_join(participant_data, questionnaires, by = c("Code" = "CODE")) %>%
  # Rename some columns
  dplyr::rename(participant_id = Code,
                BDI_Total      = BD2SUMT0, 
                OCI_Total      = OCISUMT0, 
                STAI_State     = STSSUMT0, 
                STAI_Trait     = STTSUMT0) %>%
  # Add group variable
  dplyr::mutate(group = as.factor(ifelse(substr(participant_id,13,13) == "C", "HC", "OCD")))   


# Exclude P_02 (due to retainer) and C_02 (as preregistered: patients are excluded with their match)
demographics <- demographics[demographics$participant_id != "ModERN_tDCS_P02" & demographics$participant_id != "ModERN_tDCS_C02",]


# C_12 repeated the WST at T2, because score at T1 was very low (22); score achieved at T2 was 25; we will use this score 
demographics[demographics$participant_id == "ModERN_tDCS_C12",]$WST <- 25




### Handle numeric variables

# Calculate M and SD per group 
demographics_per_group_M_SD <- demographics %>%
  dplyr::group_by(group) %>%
  # Calculate M and SD of the variables
  dplyr::summarize(across(c(Alter,WST,YBOCS_gesamt,YBOCS_Gedanken,YBOCS_Handlungen,MADRS,
                            BDI_Total,OCI_Total,STAI_State,STAI_Trait), list(mean,sd), na.rm = TRUE)) %>%
  # Reshape table to have one column per group
  gather(key = key, value = value, 2:ncol(.), factor_key = TRUE) %>% 
  spread(key = names(.)[1], value = "value") %>%
  # Add variable column
  dplyr::mutate(Variable = c("Alter", "", "WST", "", "YBOCS_Total", "", "YBOCS_Gedanken", "", "YBOCS_Handlungen", "",  "MADRS", "", "BDI_Total", "", "OCI_Total", "", "STAI_State", "", "STAI_Trait", "")) %>%
  # Add M/SD column
  dplyr::mutate(M_SD_or_n = c("M", "SD", "M", "SD", "M", "SD", "M", "SD", "M", "SD", "M", "SD", "M", "SD", "M", "SD", "M", "SD", "M", "SD")) %>%
  # Reorder columns
  dplyr::select(Variable, M_SD_or_n, HC, OCD) %>%
  dplyr::ungroup()


# Calculate t tests
demographics_per_group_t_test <- demographics %>% 
  select(Alter,WST,BDI_Total,OCI_Total,STAI_State,STAI_Trait, group) %>% 
  gather(key = Variable, value = value, -group) %>% 
  group_by(group, Variable) %>% 
  dplyr::summarise(value = list(value)) %>% 
  spread(group, value) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(Variable) %>% 
  dplyr::mutate(df = t.test(unlist(HC), unlist(OCD))$parameter,
         t_or_chi_sq_value = t.test(unlist(HC), unlist(OCD))$statistic, 
         p_value = t.test(unlist(HC), unlist(OCD))$p.value) %>%
  dplyr::select(-c(HC, OCD))  %>%
  dplyr::ungroup()


# Merge M_SD and t test infos
demographics_per_group <- left_join(demographics_per_group_M_SD, demographics_per_group_t_test, by = "Variable")




### Handle count variables

# Calculate Chi-squared tests
gender_test     <- chisq.test(demographics$Geschlecht, demographics$group)
education_test  <- chisq.test(demographics$Schulabschluss, demographics$group)
handedness_test <- chisq.test(demographics$"Händigkeit", demographics$group)


# Extract counts for gender
gender <- demographics %>% group_by(group) %>% count(Geschlecht) %>% 
  # Reshape table to have one column per group
  spread(key = names(.)[1], value = n) %>%
  # Add chi square results
  dplyr::mutate(df = ifelse(row_number()==1, gender_test$parameter, NA),
                t_or_chi_sq_value = ifelse(row_number()==1, gender_test$statistic, NA),
                p_value = ifelse(row_number()==1, gender_test$p.value, NA)) %>%
  # Add first column
  dplyr::mutate(Variable = c("Geschlecht", "")) %>%
  # Select and reorder columns
  dplyr::select(Variable, everything()) %>%
  # Rename one column to make rbind wirh columns above possible
  dplyr::rename(M_SD_or_n = Geschlecht)  %>%
  dplyr::ungroup()


# Extract counts for education
education <- demographics %>% group_by(group) %>% count(Schulabschluss, .drop = FALSE) %>% 
  # Reshape table to have one column per group
  spread(key = names(.)[1], value = n) %>%
  # Add chi square results
  dplyr::mutate(df = ifelse(row_number()==1, education_test$parameter, NA),
                t_or_chi_sq_value = ifelse(row_number()==1, education_test$statistic, NA),
                p_value = ifelse(row_number()==1, education_test$p.value, NA)) %>%
  # Add first column
  dplyr::mutate(Variable = c("Schulabschluss", "", "" , "", "" , "")) %>%
  # Select and reorder columns
  dplyr::select(Variable, everything()) %>%
  # Rename one column to make rbind wirh columns above possible
  dplyr::rename(M_SD_or_n = Schulabschluss)  %>%
  dplyr::ungroup()


# Extract counts for handedness
handedness <- demographics %>% group_by(group) %>% count(Händigkeit, .drop = FALSE) %>% 
  # Reshape table to have one column per group
  spread(key = names(.)[1], value = n) %>%
  # Add chi square results
  dplyr::mutate(df = ifelse(row_number()==1, handedness_test$parameter, NA),
                t_or_chi_sq_value = ifelse(row_number()==1, handedness_test$statistic, NA),
                p_value = ifelse(row_number()==1, handedness_test$p.value, NA)) %>%
  # Add first column
  dplyr::mutate(Variable = c("Händigkeit", "", "")) %>%
  # Select and reorder columns
  dplyr::select(Variable, everything()) %>%
  # Rename one column to make rbind wirh columns above possible
  dplyr::rename(M_SD_or_n = Händigkeit)  %>%
  dplyr::ungroup()



# Display table
my_table_template(rbind(demographics_per_group[c(1,2),], gender, education, handedness, demographics_per_group[c(3:nrow(demographics_per_group)),]), caption = "Demographic and Clinical Variables")

````
<br><br>

## Overview time intervals

```{r time-intervals}

# Create df with duration between stimulation and task in one column
time <- demographics %>%
  select(Dauer_nach_tDCS_bis_Flanker_T1,Dauer_nach_tDCS_bis_Flanker_T2) %>%
  gather(key = Variable, value = seconds)

interval_mean <- seconds_to_period(mean(time$seconds, na.rm = TRUE))
interval_sd   <- seconds_to_period(sd(time$seconds, na.rm = TRUE))
interval_min  <- seconds_to_period(min(time$seconds, na.rm = TRUE))
interval_max  <- seconds_to_period(max(time$seconds, na.rm = TRUE))
```

Days between sessions: *M* = `r round(mean(demographics$Tage_zw_Sessions, na.rm = TRUE), digits = 2)` days, *SD* = `r round(sd(demographics$Tage_zw_Sessions, na.rm = TRUE), digits = 2)`, *range* = `r min(demographics$Tage_zw_Sessions)`- `r max(demographics$Tage_zw_Sessions)`.

Duration between stimulation and task: *M* = `r interval_mean$minute`:`r round(interval_mean$second,digits=0)` min, *SD* = `r interval_sd$minute`:`r round(interval_sd$second,digits=0)`, *range* = `r interval_min$minute`:`r round(interval_min$second,digits=0)`- `r interval_max$minute`:`r round(interval_max$second,digits=0)`.